--- 
title: "R for Biochemists"
author: "Brady Johnston and Somayra Mamsa"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Guide to the R programming language for wet-lab biochemists and molecular biologists."
---

# Prerequisites {-}

You'll need to know some biochemistry, by the end of this, you'll know some 
computer as well! 

```{r pupr, fig.cap="Wow, a pupper!", out.width = "80%", fig.align="center", warning=FALSE}
pupR::pupR()
```





This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
